---
title: "Mini Project 1"
format: pdf
---
```{r include = FALSE}
#setup chunk 
library(tidyverse) 
library(tidytext)
library(textdata)

covid_tweet<-read.csv("covid19_tweets.csv")
```

```{r include = FALSE}
#Unnest the words
covid_tweet_un <- covid_tweet |> 
  mutate(line = row_number()) |>
  unnest_tokens(word, text, token = "words") 
```


```{r include = FALSE}
#Filters to tweets with #covid19
covid_tweet_unimp<-covid_tweet_un|>
  mutate(has_covid_hashtag = str_detect(hashtags, ".*[Cc][Oo][Vv][Ii][Dd].*"))|>
  filter(has_covid_hashtag== TRUE)|>
  filter(!str_detect(word, "https|t\\.co"))|>
  mutate(date = str_sub(date, 1, 10),
         date = ymd(date)) #changes date variable to be a date type variable
```

```{r include = FALSE}
#removes all words in the smart stop words library 
smart_stopwords <- get_stopwords(source = "smart") 

covid_tweet_unimp_stop<-covid_tweet_unimp|>
  anti_join(smart_stopwords) |>
  count(word, sort = TRUE) |>
  filter(word != "NA")
```

#Introduction 
The summer of 2020 was a very interesting time. February of 2020 saw COVID19 lock down the world. By summer people were slowly adjusting to the new norm I seek to investigate how people were thinking about covid during that summer. I will do this by looking at Tweets from July 24th to August 30th. I would like to see how people were thinking about Covid during this time by using sentiment analysis. 

#Quick Answer 

How were people feeling during this time. Not good as you can see in the bar chart below the tweets people were sending had almost double the negative words than it had positive words. This time was a negative time in the world so this makes sense. 

```{r echo = FALSE, message = FALSE}
#Puts in Bing sentiments and makes graph comparing Number of Positive or Negative Words 
bing_sentiments <- get_sentiments(lexicon = "bing")

covid_tweet_unimp_stop|>   
  inner_join(bing_sentiments) |>
  mutate(count = str_count(word))|>
   group_by(sentiment) |>  
  summarise(total_count = sum(count, na.rm = TRUE)) |> 
  ungroup()|>
ggplot(aes(x = sentiment, y = total_count, fill = sentiment)) +
  geom_col() +
  labs(title = "Number of Positive or Negative Words",
       x = "Sentiment Type",
       y = "Total Count of Words") +
  theme_minimal()
```


```{r include = FALSE}
# Grabs Affin sentiments and produces a tibble
afinn_sentiments <- get_sentiments(lexicon = "afinn")


covid_sentiment<-covid_tweet_unimp_stop |>   
  inner_join(afinn_sentiments) |>
  count(value)|>
  rename(sentiment_score = value,
         count= n)|>
  print()
```



```{r echo = FALSE}
#Makes histogram of sentiments from the afinn scores 
covid_sentiment|>
  ggplot(aes(x=sentiment_score, y= count))+
  geom_bar(stat = "identity")+
  labs(title = "Number of Words with Certain Sentiments",
       x= "Sentiments",
       y= "Number of Words") +
  theme_minimal()
```

```{r echo = FALSE, message = FALSE}
#shows the average afinn sentiment per day 
covid_tweet_unimp|> #cant use covid sentiments so remakes covid sentiments 
  anti_join(smart_stopwords)|>
  inner_join(afinn_sentiments)|>
  group_by(date) |>
  summarise(average_sentiment = mean(value, na.rm = TRUE)) |> # makes averages
  ungroup()|>
  ggplot(aes(x = date, y = average_sentiment)) +
  geom_line(color = "blue") + 
  geom_hline(yintercept = 0, color = "red", linetype = 2)+ #highlights where 0 is
  geom_point(color = "blue") +
  labs(title = "Average Sentiment Over Time",
       x = "Date",
       y = "Average Sentiment Score") +
  theme_minimal()
```






